gij bent 2

### 2025-09-28 paper/paper.qmd
Rename influence boxplot again
Remove uppercase in Julie graph title

Our influence metric is based on the priming ratio from @sevenants_investigating_2024 and hinges on logarithm and Laplace smoothing [@brysbaert_dealing_2013]. The logarithm is a key operation in order to compress the wide numeric range found in follower and following counts. Where some users have thousands of followers, some only have a few. The use of the logarithm scales this discrepancy down. In addition, we use Laplace smoothing in order to avoid division by zero, in the event that users do not follow other users. The mean influence value among our speakers is `r coefficients$influence %>% mean() %>% formatd()` (median `r coefficients$influence %>% median() %>% formatd()`). The boxplot in @fig-influence shows that our dataset generally consists of more influential figures, i.e. users who have more followers than they themselves follow people. This is expected, since broadly speaking, 90% of social media users only read, but never post themselves [@nielsen_participation_2006; related to the Pareto Principle: @juran_non_1975]. Since our dataset consists of posts, it makes sense that our dataset mainly engages with the other 10%, the active users. @fig-influence-boxplot shows the distribution of the influence metric.

@@

# Plot
ggplot(df, aes(x = time)) +
  geom_line(aes(y = s_curve, colour = "S-curve (Cumulative Adoption)"), linewidth = 1) +
  geom_line(aes(y = bell_curve, colour = "Bell Curve (Adoption Rate)"), linewidth = 1, linetype = "dashed") +
  geom_vline(data = cuts, aes(xintercept = x, colour = label), linetype = "dashed") +
  scale_colour_manual(
    name = "Legend",
    values = c("S-curve (Cumulative Adoption)" = "purple",
               "Bell Curve (Adoption Rate)" = "deeppink",
               "Innovators" = "red",
               "Early Adopters" = "orange",
               "Early Majority" = "goldenrod3",
               "Late Majority" = "darkgreen",
               "Laggards" = "blue")
  ) +
  labs(
    title = "S-curve and Bell Curve",
    x = "Time step",
    y = "Adoption percentage"
  ) +
  theme_minimal(base_size = 14)

>>>>

Our influence metric is based on the priming ratio from @sevenants_investigating_2024 and hinges on logarithm and Laplace smoothing [@brysbaert_dealing_2013]. The logarithm is a key operation in order to compress the wide numeric range found in follower and following counts. Where some users have thousands of followers, some only have a few. The use of the logarithm scales this discrepancy down. In addition, we use Laplace smoothing in order to avoid division by zero, in the event that users do not follow other users. The mean influence value among our speakers is `r coefficients$influence %>% mean() %>% formatd()` (median `r coefficients$influence %>% median() %>% formatd()`). The boxplot in @fig-influence-boxplot shows that our dataset generally consists of more influential figures, i.e. users who have more followers than they themselves follow people. This is expected, since broadly speaking, 90% of social media users only read, but never post themselves [@nielsen_participation_2006; related to the Pareto Principle: @juran_non_1975]. Since our dataset consists of posts, it makes sense that our dataset mainly engages with the other 10%, the active users.

@@

# Plot
ggplot(df, aes(x = time)) +
  geom_line(aes(y = s_curve, colour = "S-curve (Cumulative Adoption)"), linewidth = 1) +
  geom_line(aes(y = bell_curve, colour = "Bell Curve (Adoption Rate)"), linewidth = 1, linetype = "dashed") +
  geom_vline(data = cuts, aes(xintercept = x, colour = label), linetype = "dashed") +
  scale_colour_manual(
    name = "Legend",
    values = c("S-curve (Cumulative Adoption)" = "purple",
               "Bell Curve (Adoption Rate)" = "deeppink",
               "Innovators" = "red",
               "Early Adopters" = "orange",
               "Early Majority" = "goldenrod3",
               "Late Majority" = "darkgreen",
               "Laggards" = "blue")
  ) +
  labs(
    title = "S-curve and bell curve",
    x = "Time step",
    y = "Adoption percentage"
  ) +
  theme_minimal(base_size = 14)
